\documentclass[12pt]{article}
\begin{document}
\begin{center}
\textbf{Project Proposal -- How Couples Meet and Stay Together}
\textit{Catherine Weldon, Angie Pinilla, and Josh Robbins}
\end{center}
\begin{obeylines}
Factors that determine the success of couples are usually looked at from a psychological quantitative perspective. We are seeking to discover these factors through use of a large data set called How Couples Meet and Stay Together. This data set asks 4,002 couples questions spanning over a six year period about their demographics, identities, and many other questions related to their network and relationship success. A significant subset of this dataset is dedicated to the how and where couples met one another. From these questions, we seek to build a model that can predict the success of a relationship dependent upon these many factors. 
The ability to create a model that quantitatively determine factors that are important in a successful relationship could change the way we seek partners and maintain relationships. This model could serve as evidence for advice psychologists and couple?s counselors give and could also help online dating services improve algorithms that bring people together. Relationship fulfillment is considered one of the most important contributors to happiness, and if we can improve relationship success through this study, it will be well worth our time and resources. 
Given such a holistic set of demographics and attributes, we will be able to develop a relatively complex and detailed model which should provide unique insights in an area that has not seen a large amount of quantitative study. The survey contains significant sections on how couples met, where they first met, how they were introduced, and the background of each person. From this data we could even speculate as to what the best avenues are for meeting people to foster long-term success in a relationship. 

\end{obeylines}

\end{document}